\documentclass[a4paper,11pt]{article}
\pdfoutput=1
\usepackage{jinstpub}
\usepackage{fatalic-defs}
%\usepackage{lineno}
%\linenumbers

%-------------------------------------------------------------------------------
% Generic document information
%-------------------------------------------------------------------------------

% Title, abstract and document
\title{FATALIC: A novel CMOS front-end readout ASIC for the ATLAS Tile Calorimeter}

\abstract{
  The present article introduces a novel ASIC architecture, designed in the context of the ATLAS Tile Calorimeter upgrade 
  program for the High-Luminosity phase of the Large Hadron Collider at CERN. The architecture is based on radiation-tolerant 
  \SI{130}{\nm} \acrlong{cmos} technology, embedding both analog and digital processing of detector signals. A detailed 
  description of the ASIC is given in terms of motivation, design characteristics, simulated and measured performance. 
  Experimental studies, based on 24 prototype units under real particle beam conditions are also presented in order to 
  demonstrate the potential of the architecture as a reliable front-end readout electronic solution.
}

\author[]{S.~Angelidakis}
\author[]{W.M.~Barbe}
\author[]{R.~Bonnefoy}
\author[]{H.~Chanal}
\author[]{C.~Fayard}
\author[]{R.~Madar}
\author[]{S.~Manen}
\author[]{M.-L.~Mercier}
\author[]{E.~Nibigira}
\author[]{D.~Pallin}
\author[]{N.~Pillet}
\author[]{L.~Royer}
\author[]{A.~Soulier}
\author[]{R.~Vanda\"ele}
\author[]{F.~Vazeille}
\affiliation[]{Laboratoire de Physique de Clermont-Ferrand, CNRS/IN2P3, Universit\'e Clermont Auvergne}

\keywords{Front-end electronics for detector readout, Calorimeter methods}

%-------------------------------------------------------------------------------
% Title and Table of Contents
%-------------------------------------------------------------------------------
\begin{document}
\maketitle
\clearpage

\input{TeX/part1_intro.tex}
\input{TeX/part2_asic.tex}
\input{TeX/part3_cards.tex}
\input{TeX/part4_reco.tex}
\input{TeX/part5_tbeam.tex}

\section{Conclusion}
\label{sec:conclusion}
The above sections conclude the presentation of \gls{fatalic} and demonstrate the full potential of the \SI{130}{nm} CMOS 
technology, realised as a \gls{fe} readout electronic architecture, for the strenuous conditions of the HL-LHC. The three 
fast channels offer excellent performance for the processing of detector signal in the input charge up to \SI{1.2}{nC},
with a noise level of approximately \SI{8}{fC} and linearity better than 0.3\%, up to approximately \SI{850}{pC}, according
to simulation. Their performance was also probed with test-beam studies, in which \gls{fatalic} was used to measure the 
energy of electrons, muons and pions, reproducing the nominal estimation of the Tile EM scale constant as well as the
average energy loss per unit distance of muons traversing the TileCal.

The slow channel also exhibits the expected performance and was successfully used to process low amplitude currents in 
calibration scans using the \gls{cs} system, in order to correct the \gls{pmt} gains in the respective readout channels. 
At the same time, however, it exposes the limitations imposed by the CMOS technology, along with possible directions for 
improvement. The main limitation is the large, approximately \SI{7}{nA} $\sfrac{1}{f}$ noise, introduced by the input 
stage, which does not comply with the specification ($<$\SI{1}{nA}) defined for new the Tile \gls{fe} electronics. The 
adopted, current-driven architecture is not offered for further reduction of the noise, which would therefore require 
migration to a different (bi-CMOS) technology or relocation of the slow channel outside \gls{fatalic}.
%-------------------------------------------------------------------------------

\clearpage
%\acknowledgments

\bibliography{fatalic}

\end{document}

